Conditional selectivity for triplestores

### 2012-09-18 conditional/trunk/selectivity-basic.tex
section for class case
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@382 43ef1190-90fd-4dd7-a769-d0121f02b80e
mention bad spec on classpartitions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@383 43ef1190-90fd-4dd7-a769-d0121f02b80e

We also have in the special case of a given class, i.e. predicate
\rdfterm{rdf:type} or $P = a$ and $O = c$, we can use
\rdfterm{void:classPartition} (also defined in section~4.5 in
\cite{voidnote}) to find the selectivity of the triple pattern:
\begin{equation}\label{eq:selSvPaOc}
 \sel{T_{\{?~a~c\}}} =
    \frac{\rdfterm{void:classPartition/void:triples}}{|d|} .
\end{equation}

@@

>>>>

@@

\paragraph{Subject unbound, class bound}

The selectivity can be found directly in the case of a given class,
i.e. predicate \rdfterm{rdf:type} or $P = a$ and $O = c$, we can use
\rdfterm{void:classPartition} (also defined in section~4.5 in
\cite{voidnote}) to find the selectivity of the triple
pattern\footnote{The specification is unclear at this point, as it
 mentions the concept of entities, in which case
 \rdfterm{void:entities} might be used rather than
 \rdfterm{void:triples}, but we believe that this is the correct usage}:
\begin{equation}\label{eq:selSvPaOc}
 \sel{T_{\{?~a~c\}}} =
    \frac{\rdfterm{void:classPartition/void:triples}}{|d|} .
\end{equation}
